No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-02-28 2012-aqs/draft-aqs.tex
Updated AQS paper

\usepackage{amssymb,graphics} % for resolution symbol
\usepackage{longtable}

@@

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% [DONE] Add standard stars to observations table
% [DONE] Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainty analysis
% [DONE] Equivalent widths significant figures.
% - Strontium
% - Carbon
% - Distance calculations revision with B-V (if available) instead of (J-K)
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot w.r.t Zolotov simulations
% - Minor merger text
% - Conclusions
% - References

\author{Andrew R. Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Ken Freeman\altaffilmark{2}}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.  Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc. However, we find no evidence that the stream is a result of a classical disrupted globular cluster. Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk/halo with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\section{Introduction}
Galaxies are hierarchically formed through chaotic mergers of smaller systems. The Milky Way is no exception. The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events. As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions. Unsurprisingly, the velocities of stars within these `stellar streams' are sensitive to the galactic potential. As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.

% Consider adding a final sentence about the amount of work that has gone into stellar streaams
Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy to reveal any nearby substructures. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

@@

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$. The RAVE sample was binned in the same way, and the statistical significance of the observed over-density is discretized. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model. By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction model made any real difference to the detection significance.

@@

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters. While the exact formation site is still under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events and that those stars formed in a globular cluster-like environment.

@@

From high-resolution spectroscopy of five candidate Aquarius stars, four of which had sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in the data. Thus, they observed no evidence of a classical Na-O inverse correlation in the Aquarius stream.

@@

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation. If both scenarios are accurate then the undiscovered disrupting cluster might still remain, and would be relatively close by.

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 313.6		& 297.1 	& 0.1 \\
HD 44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & $-$187.0	& 161.8 	& 0.1 \\
HD 76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & $-$132.6	& 117.8		& 0.1 \\
HD 136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & \dots 	& 400 & 59.8		& $-$38.8 	& 0.1 \\
HD 141531		& 15:49:16.9 & \phn\.09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & \dots	& 350 & 17.7		& 2.8		& 0.1 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & \dots 	& 320 & 5.3			& 29.9 		& 0.1 \\

@@

\enddata
\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
\end{deluxetable*}

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and five additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reductions. Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing. Normalized orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere are corrected for telluric absorption.

@@

\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process. As a consequence of Eq. \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings. Although this approach relies on a reasonably accurate initial radial velocity correction of $<$4\,km s$^{-1}$ \--- which is easily achieved \--- it greatly improves the accuracy and robustness of the equivalent width measurements.

@@

We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included. We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.

\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{List of Line Transitions and Equivalent Width Measurements\label{tab:equivalent-widths}}
\tablehead{
	& & & & \multicolumn{5}{c}{Equivalent Width} \\

@@

	\colhead{Wavelength} &
	\colhead{Transition} &
	\colhead{LEP} &
	\colhead{$\log{gf}$} &
	\colhead{C2225316-14437} &
	\colhead{C2306265-085103} &
	\colhead{J221821-183424} &
	\colhead{J223504-152834} &
	\colhead{J223811-104126} \\
	({\AA})	& & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) 
}
\startdata 

@@

@@

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD 41667		& 4630	& 1.70	& 1.66 	& $-$1.21
				& 4605	& 1.88	& 1.44	& $-$1.16
				& \citet{gratton;et-al_2000} \\
HD 44007		& 4790	& 1.78	& 1.63	& $-$1.80
				& 4850	& 2.00 	& 2.20	& $-$1.71
				& \citet{fulbright_2000} \\

HD 76932		& 5755 & 3.85 & 1.41 & $-$1.06
				\\

HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 \\

HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 \\

HD 142948		& 4950	& 2.19	& 1.78	& $-$0.79
				& 4713 	& 2.17 	& 1.38	& $-$0.77
				& \citet{gratton;et-al_2000} \\
\\

@@

@@

A positive relationship between magnesium and aluminium can result from SN \textsc{ii} contributions to the local interstellar medium. High-resolution observations of disc stars illustrate this correlation \citep{bensby;venn}, demonstrating efficient SN \textsc{ii} mixing. Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}. Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively. Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle. This dredge up process replenishes the Mg which is expensed during the Mg-Al pathway. Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.

>>>>

\usepackage{amssymb,graphics} % for resolution symbol
\usepackage{longtable,booktabs,multirow}
\usepackage{pdflscape,rotating}

@@

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% [DONE] Add standard stars to observations table
% [DONE] Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainty analysis for a standard star
% - Uncertainty analysis for a prgram star
% [DONE] Equivalent widths significant figures.
% - Strontium
% - Carbon
% - Lanthinum? Europium?
% - Distance calculations revision with B-V (if available) instead of (J-K)
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot w.r.t Zolotov simulations
% - Minor merger text
% - Conclusions
% - References

\author{Andrew R. Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Ken Freeman\altaffilmark{2}}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.  Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc. However, we find no evidence that the stream is a result of a classical disrupted globular cluster. Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex, ranging between $\mbox{[Fe/H]} = -0.65$ to $-1.60$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk/halo with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\section{Introduction}
Galaxies are hierarchically formed through chaotic mergers of smaller systems. The Milky Way is no exception. The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events. As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions. Unsurprisingly, the velocities of stars within these `stellar streams' are sensitive to the galactic potential. As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances can trace the chemical evolution of the galaxy.
% can constrain the  precise nucleosynthesis sites where elements are forged, as well as

% Consider adding a final sentence about the amount of work that has gone into stellar streaams
Wide-field imaging surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps with precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy to reveal any nearby substructures. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient Signal-to-Noise ($S/N$) ratio, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

@@

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$. The RAVE sample was binned in the same way, discretizing the statistical significance of the observed over-density. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model. By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to be significant at the 4-$\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction rate made any real difference to the detection significance.

@@

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters. While the exact formation site is still under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events, and that those stars formed in a globular cluster-like environment.

@@

From high-resolution spectroscopy of six candidate Aquarius stars, four of which have sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in the data. Thus, they observed no evidence of a classical Na-O inverse correlation in the Aquarius stream.

@@

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation. If both scenarios are accurate then the undiscovered disrupting cluster might still remain, and would be relatively close by.

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 313.6		& 297.1 	& 0.1 \\
HD 44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & $-$187.0	& 161.8 	& 0.1 \\
HD 76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & $-$132.6	& 117.8		& 0.1 \\
HD 136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & \dots 	& 400 & 59.8		& $-$38.8 	& 0.1 \\
HD 141531		& 15:49:16.9 & \phn\.09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & \dots	& 350 & 17.7		& 2.8		& 0.1 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & \dots 	& 320 & 5.3			& 29.9 		& 0.1 \\
\hline

@@

\enddata
\tablenotetext{a}{S/N measured at 600\,nm for each target.}
\end{deluxetable*}

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and six  standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The exposure time for our program stars was 650\,s, in order to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One standard star, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reduction. Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing. Normalized orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed in March 2011 as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. However, critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere have been corrected for telluric absorption. The details of these corrections are discussed on a line-by-line basis.

@@

\noindent where the rest wavelength ($\lambda_{r}$) and profile sigma\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process. As a consequence of Eq. \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings. Although this approach relies on a reasonably accurate initial radial velocity correction of $<$4\,km s$^{-1}$ \--- which is easily achieved \--- it greatly improves the accuracy and robustness of the equivalent width measurements.

@@

We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included. We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies (Frebel et al. 2013, submitted) using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.

\begin{longtable*}{ccccccccc}
\caption{\\ List of Line Transitions and Equivalent Width Measurements} \tabularnewline
\cline{1-9}
& & & & \multicolumn{5}{c}{Equivalent Widths} \\

@@

Wavelength & Transition & $\chi$ & $\log{gf}$ & C2225316-14437 & C2306265-085103 & J221821-183424 & J223504-152834 & J223811-104126 \\
({\AA}) & & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) \\
\cline{1-9} \\
\endhead
\hline
\endfoot
\hline
\endlastfoot

@@

\hline
\end{longtable*}

@@

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD 41667		& 4630	& 1.70	& 1.66 	& $-$1.21
				& 4605	& 1.88	& 1.44	& $-$1.16
				& \citet{gratton;et-al_2000} \\
HD 44007		& 4790	& 1.78	& 1.63	& $-$1.80
				& 4850	& 2.00 	& 2.20	& $-$1.71
				& \citet{fulbright_2000} \\
HD 76932		& 5755 & 3.85 & 1.41 & $-$1.06
				& 5849 & 4.11 & \nodata & $-$0.88 
				& \citet{nissen;et-al_2000} \\
HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 
				& 4414 & 0.94 & 1.70 & $-$1.90 
				& \citet{gratton_sneden_1991} \\
HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 
				& 4280 & 0.70 & 1.60 & $-$1.68
				& \citet{shetrone_1996} \\
HD 142948		& 4950	& 2.19	& 1.78	& $-$0.79
				& 4713 	& 2.17 	& 1.38	& $-$0.77
				& \citet{gratton;et-al_2000} \\
\hline \\

@@

\begin{deluxetable}{lccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Optical Photometry \& Isochrone Distances\label{tab:distances}}
\tablehead{
	\colhead{Designation} &
	\colhead{$B$} &
	\colhead{$V$} &
	\colhead{$(B-V)_0$} &
	\colhead{Distance} \\
	& (mag) & (mag) & (mag) & (kpc) 
}
\startdata 
% C222531-144370   13.62 - 12.42
% C230626-085103	13.67 - 12.44
% J221821-183424	12.95 - 12.03
% J223504-152834	13.14 - 12.12
% J223811-104126   12.39 - 11.70
%					12.17 - 11.53
C222531-144370	& 13.75	& 12.52	& 1.20	& \nodata \\
C230626-085103	& 13.89	& 12.61	& 1.23	& \nodata \\
J221821-183424	& 13.08	& 12.13	& 0.92	& \nodata \\
J223504-152834	& 13.31	& 12.25	& 1.02	& \nodata \\
J223811-104126	& 12.69	& 11.93	& 0.73	& \nodata \\
				& 12.69	& 11.93	& 0.64\footnote{Extinction derived from interstellar Na D1 line (see \SS3.4.2)} & \nodata
\enddata
\end{deluxetable}

@@

A positive relationship between magnesium and aluminium can result from SN \textsc{ii} contributions to the local interstellar medium. High-resolution observations of disc stars illustrate this correlation \citep{bensby;venn}, demonstrating efficient SN \textsc{ii} mixing. Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium. Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively. Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle. This dredge up process replenishes the Mg which is expensed during the Mg-Al pathway. Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.
